---
title: "Neural Valuation of Anti-Drinking Campaigns and Risky Peer Influence in Daily Life"
author: "Scholz, C., Dore, B. P., Cooper, C., Falk, E. B."
date: "3/5/2019"
output: html_document
---

```{r,echo=FALSE}
# import libraries
library(lmerTest)
library(moments)
```


```{r,echo=FALSE}
# Get data
data_long=read.csv('github_data.csv',stringsAsFactors = F)
# create participant_level dataset
data_ppts<-data.frame()
for(i in unique(data_long$pID)){
  data_ppts=rbind(data_ppts,data_long[which(data_long$pID==i)[1],])
}

```

# Method

## Participants

- N for behavioral data = `r length(unique(data_ppts$pID))`
- `r sum(data_ppts$gender==2)/dim(data_ppts)[1]`% females
- N for neuroimaging data = `r length(unique(data_ppts$pID[!is.na(data_ppts$bartra_VMPFC_cons_c)]))`

## Variables

```{r, echo=FALSE}
# Prep for test-restest reliability
avg_drinks1_trt<-c()
avg_drinks2_trt<-c()
avg_valence1_trt<-c()
avg_valence2_trt<-c()

for(i in unique(data_long$pID)){
  cur_df_drinks<-data_long[which(data_long$pID==i & !is.na(data_long$nr_drinks_fp) & data_long$nr_drinks_fp>0),]
  cur_df_val<-data_long[which(data_long$pID==i & !is.na(data_long$valence_fp)),]
  
  avg_drinks1_trt[length(avg_drinks1_trt)+1]<-mean(cur_df_drinks$nr_drinks_fp[0:(dim(cur_df_drinks)[1]/2)])
  avg_drinks2_trt[length(avg_drinks2_trt)+1]<-mean(cur_df_drinks$nr_drinks_fp[((dim(cur_df_drinks)[1]/2)+1):dim(cur_df_drinks)[1]])
  avg_valence1_trt[length(avg_valence1_trt)+1]<-mean(cur_df_val$valence_fp[0:(dim(cur_df_val)[1]/2)])
  avg_valence2_trt[length(avg_valence2_trt)+1]<-mean(cur_df_val$valence_fp[((dim(cur_df_val)[1]/2)+1):dim(cur_df_val)[1]])
}

# Prep for split-half reliability
avg_drinks1_sh<-c()
avg_drinks2_sh<-c()
avg_valence1_sh<-c()
avg_valence2_sh<-c()

for(i in unique(data_long$pID)){

  cur_drinking_df<-data_long[which(data_long$pID==i & !is.na(data_long$nr_drinks_fp) & data_long$nr_drinks_fp>0),]
  first_half_drinks<-c()
  second_half_drinks<-c()
  for(r in seq(1,dim(cur_drinking_df)[1],2)){
    first_half_drinks[length(first_half_drinks)+1]<-cur_drinking_df$nr_drinks_fp[r]
    second_half_drinks[length(second_half_drinks)+1]<-cur_drinking_df$nr_drinks_fp[r+1]
  }
  cur_val_df<-data_long[which(data_long$pID==i & !is.na(data_long$valence_fp)),]
  first_half_val<-c()
  second_half_val<-c()
  for(r in seq(1,dim(cur_val_df)[1],2)){
    first_half_val[length(first_half_val)+1]<-cur_val_df$valence_fp[r]
    second_half_val[length(second_half_val)+1]<-cur_val_df$valence_fp[r+1]
  }
  
  avg_drinks1_sh[length(avg_drinks1_sh)+1]<-mean(first_half_drinks)
  avg_drinks2_sh[length(avg_drinks2_sh)+1]<-mean(second_half_drinks)
  avg_valence1_sh[length(avg_valence1_sh)+1]<-mean(first_half_val)
  avg_valence2_sh[length(avg_valence2_sh)+1]<-mean(second_half_val)
}

```


**Conversational valence**

- Split-half reliability:
```{r}
cor.test(avg_valence1_sh,avg_valence2_sh)
```
- Test-retest reliability
```{r}
cor.test(avg_valence1_trt,avg_valence2_trt)
```

**Drinking behavior**

- Split-half reliability:
```{r}
cor.test(avg_drinks1_sh,avg_drinks2_sh)
```
- Test-retest reliability
```{r}
cor.test(avg_drinks1_trt,avg_drinks2_trt)
```

```{r,echo=FALSE}
# prep for concurrent validity
data_ppts$mean_drinks_fp<-c()
for(i in unique(data_long$pID)){
  data_ppts$mean_drinks_fp[data_ppts$pID==i]<-mean(data_long$nr_drinks_fp[which(data_long$pID==i & data_long$nr_drinks_fp>0)],na.rm=T)
}
```

- Concurrent validity
```{r}
cor.test(log(data_ppts$mean_drinks_fp),log(data_ppts$typ_nr_drinks_bl))
```

- Skewness: `r skewness(data_long$nr_drinks_fp[data_long$nr_drinks_fp>0],na.rm=T)`

**Binge drinking attitudes**

- M = `r mean(data_ppts$alc_att_bl)`
- SD= `r sd(data_ppts$alc_att_bl)`

**Typical drinking behavior**

- Skewness: `r skewness(data_ppts$typ_nr_drinks_bl)`


## Daily Mobile Electronic Diary Analysis

**Conversational Influence Model**

Null-model
```{r}
summary(lmer(nr_drinks_fp_log_c~1+(1|pID)+(1|date_fp),data=data_long))
```

**Hangover Model**

Null-model
```{r}
summary(lmer(valence_fp_c~1+(1|pID)+(1|date_fp),data=data_long))
```
******
# Results

## Conversations and Drinking Behavior

**Occurrence of conversations (in % of days on which reports about conversations were available)**
```{r, echo=FALSE}
# prep data
perc_conv<-c()
for(i in unique(data_long$pID)){
  perc_conv[length(perc_conv)+1]<-sum(data_long$conv_fp[data_long$pID==i]==1,na.rm=T)/sum(!is.na(data_long$conv_fp[data_long$pID==i]))
}
```
Mean = `r mean(perc_conv)`
SD = `r sd(perc_conv)`
Range = `r range(perc_conv)`

**Average conversational valence** 

`r mean(data_long$valence_fp,na.rm=T)`, SD = `r sd(data_long$valence_fp,na.rm=T)`

**Number of typical drinking occasions**

Median: `r median(data_ppts$typ_drinking_occasions)`
Mean: `r mean(data_ppts$typ_drinking_occasions)`
SD = `r sd(data_ppts$typ_drinking_occasions)`

"During the last 12 months, how often did you usually have any kind of drink containing alcohol? By a drink we mean half an ounce of absolute alcohol (e.g. a 12 ounce can of beer, a 5 ounce glass of wine, or a drink containing 1 shot of liquor). Choose only one." 

* Every day (10)
* 5 to 6 times a week (9)
* 3 to 4 times a week (8)
*	twice a week (7)
*	once a week (6)
*	2 to 3 times a month (5)
*	once a month (4)
*	3 to 11 times in the past year (3)
*	1 or 2 times in the past year (2)
*	I did not drink any alcohol in the past year (1)

**Number of drinks per typical drinking occasion:**

Median: `r median(data_ppts$typ_nr_drinks_bl)`

"During the last 12 months, how many alcoholic drinks did you have on a typical day when you drank alcohol?"

*	25 or more drinks (10)
*	19 to 24 drinks (9)
*	16 to 18 drinks (8)
*	12 to 15 drinks (7)
*	9 to 11 drinks (6)
*	7 to 8 drinks (5)
*	5 to 6 drinks (4)
*	3 to 4 drinks (3)
*	2 drinks (2)
*	1 drink (1)
*	I didn't drink alcohol in the past year (0)

**Number of binge drinking occasions per month** 

Median: `r median(data_ppts$binges_bl)`

"During the last 12 months, how often did you have 5 or more (if you are male) or 4 or more (if you are female) drinks containing any kind of alcohol in within a two-hour period? (That would be the equivalent of at least 5 (4) twelve-ounce cans or bottles of beer, 5 (4) five-ounce glasses of wine, 5 (4) drinks with one shot of liquor or spirits.)"

*	Every day (9)
*	5 to 6 days a week (8)
*	3 to 4 days a week (7)
*	two days a week (6)
*	one day a week (5)
*	2 to 3 days a month (4)
*	one day a month (3)
*	3 to 11 days in the past year (2)
*	1 or 2 days in the past year (1)
*	0 days in the past year (0)


**Percentage of days during the field period on which drinking occured:**
```{r,echo=FALSE}
#Prep data
perc_drank<-c()
for(i in unique(data_long$pID)){
  perc_drank[length(perc_drank)+1]<-sum(data_long$nr_drinks_fp[data_long$pID==i]>0,na.rm=T)/sum(!is.na(data_long$nr_drinks_fp[data_long$pID==i]))
}
```

Mean: `r mean(perc_drank)`
SD: `r sd(perc_drank)`
Range: `r range(perc_drank)`

**Number of drinks per drinking occasion during the field period:**

Median: `r median(data_long$nr_drinks_fp[data_long$nr_drinks_fp>0],na.rm=T)`
Mean: `r mean(data_long$nr_drinks_fp[data_long$nr_drinks_fp>0],na.rm=T)`
SD: `r sd(data_long$nr_drinks_fp[data_long$nr_drinks_fp>0],na.rm=T)`
Range: `r range(data_long$nr_drinks_fp[data_long$nr_drinks_fp>0],na.rm=T)`

**Presence of drinking peers in percentage of days for which reports are available:**par
```{r, echo=FALSE}
# Prep data
perc_peers<-c()
for(i in unique(data_long$pID)){
  perc_peers[length(perc_peers)+1]<-sum(data_long$peer_pres_fp[data_long$pID==i]==1,na.rm=T)/sum(!is.na(data_long$peer_pres_fp[data_long$pID==i]))
}
```
Mean: `r mean(perc_peers)`
SD: `r sd(perc_peers)`

## Conversational Influence and Hangover Effects

**Conversational Influence Model - Table 1**

```{r}
mod1<-lmer(nr_drinks_fp_log_c~yvalence_fp_c+alc_att_bl_c+peer_pres_fp_c+typ_nr_drinks_bl_log_c+mean_valence_fp_c+gender_c+(1|pID)+(1|date_fp),data=data_long)
summary(mod1)
confint(mod1,oldNames=F)
```

**Hangover Model - Table 1**
```{r}
mod2<-lmer(valence_fp_c~ynr_drinks_fp_log_c+alc_att_bl_c+peer_pres_fp_c+typ_nr_drinks_bl_log_c+gender_c+mean_valence_fp_c+(1|pID)+(1|date_fp),data=data_long)
summary(mod2)
confint(mod2,oldNames=F)
```

## Regulation of Neural Valuation Responses to Media Messages Moderates Peer Influence

**Moderation by message-consistent regulation success - Table 1**

```{r}
mod3<-lmer(nr_drinks_fp_log_c~yvalence_fp_c*bartra_cons_c+peer_pres_fp_c+gender_c+typ_nr_drinks_bl_log_c+(1|pID)+(1|date_fp),data=data_long)
summary(mod3)
confint(mod3,oldNames=F)
```

**Moderation by message-derogating regulation success - Table 1**
```{r}
mod4<-lmer(nr_drinks_fp_log_c~yvalence_fp_c*bartra_derog_c+peer_pres_fp_c+gender_c+typ_nr_drinks_bl_log_c+(1|pID)+(1|date_fp),data=data_long)
summary(mod4)
confint(mod4,oldNames=F)
```

**VMPFC - Moderation by message-consistent regulation success - Table 2**
```{r}
mod3a<-lmer(nr_drinks_fp_log_c~yvalence_fp_c*bartra_VMPFC_cons_c+peer_pres_fp_c+gender_c+typ_nr_drinks_bl_log_c+(1|pID)+(1|date_fp),data=data_long)
summary(mod3a)
confint(mod3a,oldNames=F)
```

**VMPFC - Moderation by message-derogating regulation success - Table 2**
```{r}
mod3b<-lmer(nr_drinks_fp_log_c~yvalence_fp_c*bartra_VMPFC_derog_c+peer_pres_fp_c+gender_c+typ_nr_drinks_bl_log_c+(1|pID)+(1|date_fp),data=data_long)
summary(mod3b)
confint(mod3b,oldNames=F)
```

**VS - Moderation by message-consistent regulation success - Table 2**
```{r}
mod4a<-lmer(nr_drinks_fp_log_c~yvalence_fp_c*bartra_VS_cons_c+peer_pres_fp_c+gender_c+typ_nr_drinks_bl_log_c+(1|pID)+(1|date_fp),data=data_long)
summary(mod4a)
confint(mod4a,oldNames=F)
```
**VS - Moderation by message-derogating regulation success - Table 2**
```{r}
mod4b<-lmer(nr_drinks_fp_log_c~yvalence_fp_c*bartra_VS_derog_c+peer_pres_fp_c+gender_c+typ_nr_drinks_bl_log_c+(1|pID)+(1|date_fp),data=data_long)
summary(mod4b)
confint(mod4b,oldNames=F)
```

**Models including the cognitive regulation ROI**
```{r}
mod5<-lmer(nr_drinks_fp_log_c~yvalence_fp_c*omnibus_condeff_cons_c+peer_pres_fp_c+gender_c+typ_nr_drinks_bl_log_c+(1|pID)+(1|date_fp),data=data_long)
summary(mod5)
confint(mod5,oldNames=F)

mod6<-lmer(nr_drinks_fp_log_c~yvalence_fp_c*omnibus_condeff_derog_c+peer_pres_fp_c+gender_c+typ_nr_drinks_bl_log_c+(1|pID)+(1|date_fp),data=data_long)
summary(mod6)
confint(mod6,oldNames=F)
```


# Supplementary Materials
"Note that for all models describd here, main results of interest remain unchanged in direction and magnitude when excluding all covariates from the models."

*Table S1*
```{r}
mod1_nocov<-lmer(nr_drinks_fp_log_c~yvalence_fp_c+(1|pID)+(1|date_fp),data=data_long)
summary(mod1_nocov)
confint(mod1_nocov,oldNames=F)

mod2_nocov<-lmer(valence_fp_c~ynr_drinks_fp_log_c+(1|pID)+(1|date_fp),data=data_long)
summary(mod2_nocov)
confint(mod2_nocov,oldNames=F)

mod3_nocov<-lmer(nr_drinks_fp_log_c~yvalence_fp_c*bartra_cons_c+(1|pID)+(1|date_fp),data=data_long)
summary(mod3_nocov)
confint(mod3_nocov,oldNames=F)

mod4_nocov<-lmer(nr_drinks_fp_log_c~yvalence_fp_c*bartra_derog_c+(1|pID)+(1|date_fp),data=data_long)
summary(mod4_nocov)
confint(mod4_nocov,oldNames=F)
```

*Table S2*
```{r}
mod3a_nocov<-lmer(nr_drinks_fp_log_c~yvalence_fp_c*bartra_VMPFC_cons_c+(1|pID)+(1|date_fp),data=data_long)
summary(mod3a_nocov)
confint(mod3a_nocov,oldNames=F)

mod3b_nocov<-lmer(nr_drinks_fp_log_c~yvalence_fp_c*bartra_VS_cons_c+(1|pID)+(1|date_fp),data=data_long)
summary(mod3b_nocov)
confint(mod3b_nocov,oldNames=F)

mod4a_nocov<-lmer(nr_drinks_fp_log_c~yvalence_fp_c*bartra_VMPFC_derog_c+(1|pID)+(1|date_fp),data=data_long)
summary(mod4a_nocov)
confint(mod4a_nocov,oldNames=F)

mod4b_nocov<-lmer(nr_drinks_fp_log_c~yvalence_fp_c*bartra_VS_derog_c+(1|pID)+(1|date_fp),data=data_long)
summary(mod4b_nocov)
confint(mod4b_nocov,oldNames=F)
```

*Table S3*
```{r}
mod5_nocov<-lmer(nr_drinks_fp_log_c~yvalence_fp_c*omnibus_condeff_cons_c+(1|pID)+(1|date_fp),data=data_long)
summary(mod5_nocov)
confint(mod5_nocov,oldNames=F)

mod6_nocov<-lmer(nr_drinks_fp_log_c~yvalence_fp_c*omnibus_condeff_derog_c+(1|pID)+(1|date_fp),data=data_long)
summary(mod6_nocov)
confint(mod6_nocov,oldNames=F)
```

